|

### 2020-09-21 paper.Rmd
style package names consistently

Here we compare the sage display and regular tour display on mouse retinal single cell RNA-seq data from
@Macosko2015-ot. The raw data consists of a 49,300  cells and was downloaded
using the using the **scRNAseq** Bioconductor package [@scRNAseq-d]. We
use a standard workflow for pre-processing and normalizing this data 
(described by @Amezquita2020-at): we performed quality control using the **scater** package [@McCarthy2017]
and we log-transformed and normalised the expression 
values and selected highly variable genes (HVGs) using **scran** 
[@Lun2016]. The top ten percent of most HVGs were used as features to subset
the normalised expression matrix and compute principal components.
Using the first 25 PCs we built a shared nearest neighbours graph (with $k = 10$) and 
clustered this graph using Louvain clustering, resulting in 11 clusters being formed [@Blondel2008-bx].

>>>>

Here we compare the sage display and regular tour display on mouse retinal single cell RNA-seq data from
@Macosko2015-ot. The raw data consists of a 49,300  cells and was downloaded
using the using the `scRNAseq` Bioconductor package [@scRNAseq-d]. We
use a standard workflow for pre-processing and normalizing this data 
(described by @Amezquita2020-at): we performed quality control using the `scater` package [@McCarthy2017]
and we log-transformed and normalised the expression 
values and selected highly variable genes (HVGs) using `scran` 
[@Lun2016]. The top ten percent of most HVGs were used as features to subset
the normalised expression matrix and compute principal components.
Using the first 25 PCs we built a shared nearest neighbours graph (with $k = 10$) and 
clustered this graph using Louvain clustering, resulting in 11 clusters being formed [@Blondel2008-bx].
